%
%  Abstract
%

\begin{abstract}
\addcontentsline{toc}{chapter}{Abstract}
%todo: max 350 words

This dissertation describes a search for $R$-parity violating supersymmetry, motivated by the stringent limits set on $R$-parity conserving models from Run I and Run II of the LHC.
These limits have excluded gluno masses up to approximately 2~\TeV in mass, which is the rough scale expected for supersymmetry to ``naturally'' solve the Hierarchy Problem.
These constraints, however, can be evaded by considering $R$-parity violating models, in which the lightest supersymmetric particle can decay to Standard Model particles and do not produce large missing transverse momentum signatures.

To avoid conflicts with experimental measurements, such as proton decay, the framework of Minimal Flavor Violation is applied, resulting in the largest $R$-parity violating coupling being between a top, bottom, and strange quark.
Because of this, this search uses the pair production of gluinos that decay via \rpvDecay as a benchmark model and generically looks for new physics with a signature of a single lepton, large jet and bottom quark jet multiplicities, and high sum of large-radius jet masses, without any requirement on the missing transverse momentum in an event.

The search is conducted with $35.9~\ifb$ of $\sqrt{s} = 13~\TeV$ proton-proton collisions collected by the CMS experiment in 2016.
The background is estimated through a maximum-likelihood fit of the \Nb distribution across bins of jet multiplicity and sum of large-radius jet masses.
No evidence of new physics is observed, and limits on a simplified model, in which gluinos decay promptly via \smsDecay, are set, excluding gluino masses below 1610~\GeV at the 95\% confidence level.

%\abstractsignature
\end{abstract}


