\begin{acknowledgements}

Since my childhood, I have always been fascinated by big questions about the universe, and I feel blessed to have had the opportunity to immerse myself in them for the past five years.
This dissertation encapsulates my career as a particle physicist and my contribution to answering those universal questions.
I, however, could not have done this without many helping hands to whom I owe a great deal.

First, I must thank the RichStu group---my HEX family. 
In particular, I want to thank my advisor, David Stuart, for always being a fantastic mentor, and Jeff Richman, my de facto second advisor, for his extraordinary teaching.
There is not enough space here to properly thank you for all your guidance and wisdom.
I would not be the physicist I am today without it.
To the postdocs---Ana Ovcharova, Chris West, Jae Hyeok Yoo, Manuel Franco Sevilla, and Matt Citron---and to my fellow graduate students in arms---Adam Dishaw, Alex Dorsett, Jack Bradmiller-Feld, and Ryan Heller---it was truly a pleasure to have gone through this Ph.D. with all of you.
I could not have asked for a better group of colleagues and friends.
You made grad school fun, and I'll always have fond memories of the hour-long impromptu discussions we found ourselves in, whether we were debating physics, the news, or, far more often, color themes.

I also owe much gratitude to my parents, Ramesh and Savita, without whom none of this would be possible.
It was only through their endless love and support and countless sacrifices that I was able to pursue my dreams.
Included in this is my brother, Simit, who was always willing to make time for me and share his advice.

Finally, I would like to thank my partner, Mallorie Chase, for all her support over the last few years and for moving with me to Geneva for a year-long adventure.
I am so thankful to have met you during my time here, and I am excited to tackle our next chapter in life together.

\end{acknowledgements} 
